---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# repo.data

<!-- badges: start -->
[![R-CMD-check](https://github.com/llrs/repo.data/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/llrs/repo.data/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/llrs/repo.data/graph/badge.svg)](https://app.codecov.io/gh/llrs/repo.data)
<!-- badges: end -->

The goal of repo.data is to make repository data accessible. 
Mainly it consumes existing data but the idea is to also generate it.

When a function is specific of a repository it will start with its name: `cran_` or `bioc_`.

## Installation

From CRAN:

``` r
install.packages("repo.data")
```

You can install the development version of repo.data like so:

``` r
remotes::install_github("llrs/repo.data")
```



## Example

We can get a data.frame of all packages on CRAN archive:

```{r example}
library(repo.data)
ca <- cran_archive()
head(ca)
```

We can also check CRAN comments about the packages on its archive:

```{r cran_comments}
cc <- cran_comments()
head(cc)
```

Or estimate the last date of update of our packages, by the information on the session info or a data.frame:

```{r cran_dates}
cran_session(session = sessionInfo())
ip <- installed.packages()
cran_date(ip)
```

## Related packages

Other packages and related analysis :

- Task views: https://github.com/epiverse-connect/ctv-analysis/
- static packages: [pkgstats](https://docs.ropensci.org/pkgstats/)
- Bioconductor: biopkgtools
- R-universe: universe
- [cranly](https://cran.r-project.org/package=cranly): About package dependencies and authors of packages.
- [versions](https://github.com/goldingn/versions): A package about installing packages versions.
 `install.dates()` requires a CRAN date, if you are unsure you can use `cran_date()` to estimate it given a `library()` or a `sessionInfo` report.
- [checkpoint](https://cran.r-project.org/package=checkpoint) provides tools to ensure the results of R code are repeatable over time.

## History

This package comes from the analysis on CRAN data on https://llrs.dev
