---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# repo.data

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/repo.data)](https://CRAN.R-project.org/package=repo.data)
<!-- badges: end -->

The goal of repo.data is to make repository data accessible. 
Mainly it consumes existing data but the idea is to also generate it.

## Installation

You can install the development version of repo.data like so:

``` r
remotes::install_github("llrs/repo.data")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(repo.data)
ca <- cran_archive()
head(ca)
```

We can also check CRAN comments 

```{r cran_comments}
cc <- cran_comments()
head(cc)
```


## Related packages

Other packages and related analysis :

- Task views: https://github.com/epiverse-connect/ctv-analysis/
- static packages: [pkgstats](https://docs.ropensci.org/pkgstats)
- Bioconductor: biopkgtools
- R-universe: universe

## History

This package comes from the analysis on CRAN data on https://llrs.dev
